The Etiology of Cybersecurity

### 2020-09-02 reports/paper_0/main.tex
anonymize ref to github repo

As already presented in \autocite{Santaca2016abf}, it follows that, defining
a system with a fixed number of regions, there exist
an upper-bound to the number of possible configuration of a system, defined by
the possible relations between the different regions.
For completeness, we report in the next paragraph 
the calculation done in \autocite{Santaca2016abf}.

@@

\subsection{Cybersecurity Risk Assessment}\label{sec:secra}
In order to test our hypothesis we implemented a tool-chain (open-source under the
AGPLv3 license and available at \autocite{v-research2020cybersecurity}) for the
identification of weaknesses and the precise calculation of potential insecure
configurations. The engineering of the $\abftheory$-framework for CPS is summarized in the UML
Class diagram in Figure~\ref{fig:secraclassdiagram} (in appendix).

>>>>

As in \autocite{Santaca2016abf}, it follows that, defining
a system with a fixed number of regions, there exist
an upper-bound to the number of possible configuration of a system, defined by
the possible relations between the different regions.
For completeness, we report in the next paragraph 
the calculation done in \autocite{Santaca2016abf}.

@@

\subsection{Cybersecurity Risk Assessment}\label{sec:secra}
In order to test our hypothesis we implemented a tool-chain (open-source under the
AGPLv3 license and available at \autocite{v-research2020cybersecurity-anonymous}) for the
identification of weaknesses and the precise calculation of potential insecure
configurations. The engineering of the $\abftheory$-framework for CPS is summarized in the UML
Class diagram in Figure~\ref{fig:secraclassdiagram} (in appendix).
